\documentclass[conference]{sig-alternate-10pt}

\usepackage[tight,footnotesize]{subfigure}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{times}
\usepackage{graphics}
\usepackage{graphicx}
\usepackage{epstopdf}
%\usepackage{slashbox}

\usepackage{epsfig}
\usepackage{amstext}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{url}
\usepackage{psfrag}
\usepackage{verbatim}
\usepackage{color}
%\usepackage{hyperref}
\usepackage[bf]{caption}

\newtheorem{lemma}{Lemma}
\newtheorem{theorem}{Theorem}
\newtheorem{proposition}{Proposition}
\newtheorem{conjecture}{Conjecture}
\newtheorem{definition}{Definition}

\newcommand {\bear}{\begin{eqnarray}}
\newcommand {\eear}{\end{eqnarray}}
\newcommand {\bearn}{\begin{eqnarray*}}
\newcommand {\eearn}{\end{eqnarray*}}
\newcommand {\barr}{\begin{array}}
\newcommand {\earr}{\end{array}}
\newcommand {\done} {\hfill\quad\vrule height4pt WIDTH4PT}
\def\cee#1#2{\left(\barr{c} #1\\ #2 \earr \right)}
\def\tA{\tilde{A}}
\def\tL{\tilde{L}}
\def\tM{\tilde{M}}
\def\tP{\tilde{P}}
\def\real{{\rm I\!R}}
\def\cS{{\cal S}}
\def\cF{{\cal F}}
\def\hT{\hat{T}}
\def\b1{\mathbf{1}}
%\def\hr{\hat{R}}
%\def\RR{\mathbb{R}}


\newcommand{\la}{\lambda}
\newcommand{\al}{\alpha}
\newcommand{\be}{\begin{equation}}
\newcommand{\ee}{\end{equation}}
\newcommand{\bi}{\begin{itemize}}
\newcommand{\ei}{\end{itemize}}
\def\bearn{\begin{eqnarray*}}
\def\eearn{\end{eqnarray*}}
\def\bheader#1{\noindent{\bf #1}}
\def\bie#1{\item{\bf{#1}}}

\newcommand{\bmax}{\mathop{\boldsymbol{\max}}}
\newcommand{\bmin}{\mathop{\boldsymbol{\min}}}
\newcommand{\bargmax}{\mathop{\mathbf{argmax}}}
\newcommand{\bargmin}{\mathop{\mathbf{argmin}}}

%%%%%%%%%%%%%%%from harald
\newcommand{\hide}[1]{}

\newcommand{\fix}{\marginpar{FIX}}
\newcommand{\new}{\marginpar{NEW}}
\newcommand{\RR}{\mathbb{R}}
\newcommand{\NN}{\mathbb{N}}
\newcommand{\tr}{{\rm tr}}
\newcommand{\tU}{P}
\newcommand{\tV}{Q}
\newcommand{\tW}{{\tilde{W}}}
\newcommand{\tR}{{\tilde{R}}}
\newcommand{\ba}{{\bf a}}
\newcommand{\bb}{{\bf b}}
\newcommand{\bd}{{\bf d}}
\newcommand{\identity}{I}
\newcommand{\ones}{{1\!\!1}}
\newcommand{\elprod}{\otimes}
\newcommand{\WMW}{{\rm WMW}}
\newcommand{\stepfct}{{\bf 1}}
\newcommand{\hy}{\hat{Y}}
\newcommand{\hr}{\hat{R}}
\newcommand{\rimp}{R^{\rm o\& i}}
\newcommand{\rank}{{\rm Rank}}
\newcommand{\nrank}{{\rm Nrank}}
\newcommand{\anr}{{\rm ANR}}
\newcommand{\aanr}{{\rm A}^{\rm 2}{\rm NR}}
\newcommand{\pr}{ \bar{R}}
\newcommand{\rmse}{{\rm RMSE}}
\newcommand{\Robs}{R^{\rm obs}}
\newcommand{\topk}{{\rm TOPK}}
\newcommand{\areatop}{{\rm ATOP}}
\newcommand{\ppp}{{\rm Prec}_u @ }
\newcommand{\rrr}{{\rm Rec}_u @ }
\newcommand{\sN}{\tilde{N}}
\newcommand{\mult}{} %\cdot
\newcommand{\auc}{{\rm AUC}} %\cdot
\newcommand{\gauss}{{\cal N}} %\cdot
\newcommand{\Qi}{i} %\cdot
\newcommand{\hQ}{\hat{Q}} %\cdot
\newcommand{\hP}{\hat{P}} %\cdot
\newcommand{\hM}{\hat{M}} %\cdot
\newcommand{\precision}{{\rm P}} %\cdot
\newcommand{\recall}{{\rm R}} %\cdot
\newcommand{\ndcg}{{\rm nDCG}} %\cdot
\newcommand{\dcg}{{\rm DCG}} %\cdot
\newcommand{\sdcg}{{\rm sDCG}} %\cdot
\newcommand{\err}{{\rm ERR}} %\cdot
\newcommand{\map}{{\rm MAP}} %\cdot
\newcommand{\popcount}{{\rm pop}} %\cdot
\newcommand{\countall}{{\rm \# ratings}} %\cdot
\newcommand{\hitrate}{{\rm HR}} %\cdot
\newcommand{\ic}{i_0} %number of items
\newcommand{\uc}{u_0} %number of users
\newcommand{\jc}{j_0} %rank of low-rank MF, or latent dimensions


\newcommand{\cc}{CircleCon} %rank of low-rank MF, or latent dimensions
\newcommand{\com}[1]{{\color{red}\bf #1}}
\newcommand{\ci}{{\cal C}}
\newcommand{\cat}{{\rm cat}}

%%%----------------------- make it tighter ----------------------------
%\topskip -0.5in            %between header and text
%\parskip 0in            %gap between paragraphs
%\floatsep 0.1in           %space left between floats
%\textfloatsep 0.1in       %space between last top float or first bottom float and the text
%\intextsep 0.1in          %space left on top and bottom of an in-text float
%\dblfloatsep 0.1in        %floatsep for 2 column
%\dbltextfloatsep 0.05in    %space between last top float or first bottom float and the text
%\abovecaptionskip 0.01in   %space above caption
%\belowcaptionskip 0.02in   %space below caption
%\abovedisplayskip 0.1in   %space before maths
%\belowdisplayskip 0.1in   %space after maths
%\arraycolsep 0in       %gap between columns of an array
%\topsep 0in             %space between first list item and preceding paragraph.
%\partopsep 0.1in          %extra space added to \topsep when environment

%\ifCLASSINFOpdf
%  \graphicspath{{./fig/}}
%\else
%\fi

%\hyphenation{op-tical net-works semi-conduc-tor}

\begin{document}
%\conferenceinfo{CoNEXT'12,} {December 10--13, 2012, Nice, France.}
%\CopyrightYear{2012}
%\crdata{978-1-4503-1775-7/12/12}
%\clubpenalty=10000
%\widowpenalty = 10000

\title{Multipath IP transmission: Motivation, Design, Performance}

%\author{
%\alignauthor Guibin Tian and Yong Liu\\
%        \affaddr{Department of Electrical and Computer Engineering}\\
%        \affaddr{New York University Polytechnic School of Engineering}\\
%        \affaddr{Brooklyn, NY, USA 11201}\\
%        \email{gt680@nyu.edu, yongliu@poly.edu}
%}

\maketitle


\begin{abstract}
%\boldmath
Multipath Internet transmission has become available in recent years. Most devices have more than one interfaces that can connect to Internet. Especially the booming of mobile devices introduces the greatest chance for multipath communication.

In $2011$, multipath TCP was introduced as RFC by IETF. This draft defines the architecture and guideline of multipath TCP development. Also, a popular multipath TCP implementation\cite{mptcp} has been in process for several years. Most recent research on multipath is based on this implementation. But, as the name refers, multipath TCP is only designed for TCP traffic. Inside the current Internet infrastructure, it is still an accepted assumption that most Internet traffic is transmitted via the TCP protocol. However, the rise of new streaming applications and P$2$P protocols that try to avoid traffic shaping techniques will likely increase the use of other protocols like UDP as a transport protocol.

In this paper, we introduce multipath communication at network layer instead of transmission layer. By introducing multipath capability at network layer, almost all traffic on Internet can benefit from multipath. Also, in the kernel of any operation system, because the huge difference of complexity between TCP and IP, we can expect a much lighter weighted implementation of multipath at network layer. To evaluate the performance of MPIP, we implement our proposition in the latest Linux kernel under Ubuntu system. We prove that besides having the same even better performance as MPTCP for TCP traffic, MPIP also has good support to UDP traffic, and provides potential optimized routing decision for specific applications.

\end{abstract}

%\category{H.5.1}{Information Systems}{Multimedia Information Systems}[Video(e.g., tape, disk, DVI)]
%\terms{Design}
%\keywords{Adaptation, DASH, Emulab, Multiple CDN, SVR}
%\IEEEpeerreviewmaketitle

\input{intro}
\input{related}
\input{design}
\input{evaluation}

\section{Conclusions and Future Work}
\label{sec:conclusion}

Given the popular support of multiple network interfaces on modern devices, MPIP is designed to make full of each interface to achieve optimal performance. Besides higher throughput than single path transmission, customized routing for specific application's requirement is also in the consideration of MPIP when designing the system. Instead of sole support of TCP traffic, MPIP works with any upper protocol that use regular IP as the transmission method, i.e. TCP and UDP.

In the work, we prove that multipath can be implemented at network layer with less effort and better maintainability because of the simplicity of network layer. According to our evaluation, besides higher throughput than regular TCP, customized routing capability can greatly benefit applications that have different requirement of high throughput and high responsiveness. By combing MPTCP and MPIP together, with the support of MPTCP's unique two-layer sequence number management and independent TCP subflow mechanism, we surprisingly achieved the best throughput result.

We can see that with unstable connections like $4$G, MPIP's performance is yet satisfactory. We use a simple delay-based path selection algorithm in this prototype, a more complete and efficient module can be designed for this functionality in the future. Also, customized routing now only supports packet length based decision, a smarter decision mechanism like flow-table in SDN is under consideration. As future works, Android implementation is next step to directly use $4$G interface instead of hotspot access. IPv6 support is also another feature that is underway.

\bibliographystyle{./bib/IEEEtran}
\bibliography{./bib/IEEEfull}
\end{document}


