%!TEX root =mpip.tex
\section{Related Work}
\label{sec:related}
Multipath transmission has been attracting research interest for quite some time. Back to $2001$, Hsieh et al proposed pTCP\cite{hsieh01} that effectively performs bandwidth aggregation on multi homed mobile hosts with simulation results. In \cite{key01}, the authors investigated the potential benefits of coordinated congestion control for multipath data transfers as well as relative path selection algorithm when multipath is available. In \cite{dong01}, Dong et al implemented concurrent TCP(cTCP) in FreeBSD to improve throughput of connections through balancing traffic load on multiple end-to-end paths. The Stream Control Transmission Protocol (SCTP)\cite{sctp} is designed with multihoming to support failover instead of parallel transmission. In \cite{joe01}, Joe et al extends SCTP to support simultaneous transmission with best load-sharing and achieve throughput improvement.

In $2010$, Barre et al published an experimental result of using multiple paths simultaneously in TCP transmission\cite{BRBH10}. After two years, the same team released the first public implementation of multipath TCP in \cite{mptcp}. In \cite{mptcp}, according to RFC $6182$ released by IETF specifically for multipath TCP in $2011$, the authors implemented a complete prototype of multipath TCP in Linux and Android system. They also explored many other aspects of MPTCP in \cite{PDDRB12}, \cite{DPLMAB13}, \cite{PKB13}, \cite{PFAB14}.

Base on this prototype, many researches that focus on measurement and improvement of MPTCP join the research of multipath. In \cite{chen01}, based on WiFi and cellular network Chen et al did a thorough measurement of MPTCP over wireless environment. They considered multiple cellular network providers to do complete side-by-side comparison. In \cite{cao01}, a delay-based congestion control algorithm which is a transformation of Vegas\cite{vegas} was proposed for multipath TCP.

At router level, ECMP\cite{ecmp} supports load balancing of general IP packets among different paths between two routers. But ECMP need router's support and doesn't work on end hosts.

In industry, Apple\cite{apple} implements multipath TCP in iOS $7.0$ for its siri, cloud-based natural language voice command and navigation service which is the first large-scale deployment of multipath TCP.